Simulation of Tsunami impact upon Coastline

### 2016-02-17 paper/paper.tex
Final report, paper review draft.

\section{Conclusions}
We presented the theoretical background and implementation of an enriched SPH framework,
whose main purpose was the faithful simulation and detailed recording of the forces
exerted upon the coastline during a tsunami impact. The chosen output file format lends
itself for rich visualizations, allowing for a quick overview of complex simulation data.

>>>>

\section{Conclusions}
We presented the theoretical background and implementation of an enriched SPH framework,
whose main purpose was the faithful simulation and detailed recording of the forces
exerted upon the coastline during a tsunami impact. The chosen output file format lends
itself to rich visualizations, allowing for a quick overview of complex simulation
data. Multiple simulations have been carried out, resulting in interesting visualizations
of impact data and evaluation of defense mechanisms. Furthermore, detailed impulse logs
are provided, which can then be processed to extract relevant high level
information. Possible future extensions could be the incorporation of wider, dynamic
terrain models, including nearby seabed, the adjustment of the fluid initial conditions to
match those predicted by large-scale shallow water models, and performance optimizations
in the implementation towards a more integrated dataflow scheme.
